### 2016-01-21 paper-arxiv-v2/sec-mva.tex
Revised version of paper

At the end of the loose cut-based analysis,
by combining the three event topologies,
we obtain a signal significance of $S/\sqrt{B}\simeq 0.8~(1.4)$
with all backgrounds (only QCD $4b$) considered.
%
This section describes how this signal significance
 can be enhanced when the cut-based analysis
 is complemented by multivariate techniques.
%
 These are by now a mature tool
 in high-energy physics data analysis, opening
 new avenues to improve the performance
of many measurements and searches at high-energy colliders.
%
In particular, the classification of events into
signal and
background processes by means of MVAs is
commonly used in LHC
applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
  Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{plots/res_wgthist_noPU.pdf}
\includegraphics[width=0.49\textwidth]{plots/int_wgthist_noPU.pdf}
\includegraphics[width=0.75\textwidth]{plots/bst_wgthist_noPU.pdf}
\vspace{-0.5cm}
\caption{\small
Distribution of the total associated weight,
Eq.~(\ref{eq:totweight}) for each of the $N_{\rm var}$ input
variables of the resolved (upper left),  intermediate (upper right)
and boosted (lower plot)
categories.
}
\label{fig:nnweights}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

>>>>

At the end of the loose cut-based analysis,
by combining the three event topologies,
we obtain a signal significance of $S/\sqrt{B}\simeq 0.8~(1.4)$
with all backgrounds (only QCD $4b$) considered.
%
This section describes how this signal significance
 can be enhanced when the cut-based analysis
 is complemented by multivariate techniques.
%
 These are by now a mature tool
 in high-energy physics data analysis, opening
 new avenues to improve the performance
of many measurements and searches at high-energy colliders.
%
In particular, the classification of events into
signal and
background processes by means of MVAs is
commonly used in LHC
applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
  Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia,Kang:2015uoc}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{plots/res_wgthist_noPU.pdf}
\includegraphics[width=0.49\textwidth]{plots/int_wgthist_noPU.pdf}
\includegraphics[width=0.60\textwidth]{plots/bst_wgthist_noPU.pdf}
\vspace{-0.5cm}
\caption{\small
Distribution of the total associated weight,
Eq.~(\ref{eq:totweight}) for each of the $N_{\rm var}$ input
variables of the resolved (upper left),  intermediate (upper right)
and boosted (lower plot)
categories.
}
\label{fig:nnweights}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
